Comparing tool variability and numerical variability in fMRI analyses

### 2021-11-26 paper/paper.tex
Update result section

Further, from the thresholded maps, we determined regional Dice
coefficients between activation clusters in the 360 regions in the Human
Connectome Project Multi-Modal Parcellation atlas version 1.0
(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, Dice coefficients were
computed between activation maps produced by any pair of tools. For WT,
Dice coefficients were computed pair-wise among the three Fuzzy samples of
a given tool and averaged. All Dice coefficients were normalized by the
region size \tristan{explain how you did this: x = (dice x region size) ; x = (x-xmin)/(xmax-xmin)}.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually imperceptible. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
Overall, our results correctly reproduced
the ones presented in~\cite{bowring2019exploring}. The observed
differences were small and might be due to the use of Octave vs MATLAB in
SPM, different operating systems \tristan{had you checked that?}, or
different hardware. We performed visual quality control of the AFNI and SPM results
for each individual subject.
\tristan{add a figure to show the differences for SPM (Octave) and AFNI}

@@

Summary statistics for the group-level unthresholded and thresholded
t-statistics are reported in Table~\ref{table:pipeline-stats}.
\tristan{From here this paragraph needs a full re-write} Overall, BT
variability was larger than WT variability for both means and standard
deviations \tristan{I don't think it's the case for stdev}. This was
confirmed by computing the T-test and Wilcoxon signed-rank statistics
between $BT(A, B)$, and $WT(A)$ and $WT(B)$ for $A$ and $B$ in $[FSL, SPM,
AFNI]$. We obtained statistically significant values between BT and WT
variability with t-value $> 70$ and p-value $< 0.05$ in both thresholded
and unthresholded maps.

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc|cc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \cmidrule{5-6} \\
        {} & {} & Mean & Std. dev. & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  \\
        \bottomrule
    \end{tabular}
    \caption{Summary of voxel-wise mean and standard deviation in
    group-level t-statistics in BT and WT \tristan{The caption doesn't
    reflect what I thought this table represented, this needs
    discussion. Also in Table III.}.}
    \label{table:pipeline-stats}
\end{table}

@@

  %%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \\
        {} & {} & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  0.366       & 0.293     \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  0.439       & 0.352     \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.048       & 0.037     \\
        {}   & AFNI                          &  0.108       & 0.131     \\
        \bottomrule
    \end{tabular}
    \caption{Summary of voxel-wise mean and standard deviation in subject-level t-statistics in BT and WT. Values were averaged across 16 subjects.}
    \label{table:unthresh-maps-subjects}
\end{table}

@@

  Similar conclusions are drawn from the unthresholded t-statistics maps
  (Figure~\ref{fig:thresh-maps}).  Figure~\ref{fig:dice-thresh} compares regional normalized Dice coefficients of
  activated voxels, showing a linear correlation between BT and WT with
  p-value $< 0.05$ in all three pairs.

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}. \tristan{Change the column headers to (FSL, SPM) instead of FSL - SPM (everywhere).}}
      \label{fig:thresh-maps}
      \end{minipage}}
    \end{figure*}

    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
    \begin{figure*}[ht]
      \centering
      \includegraphics[width=\textwidth]{figures/dices_corr.png}
      \caption{Normalized regional Dice coefficients of activated voxels for
      BT and WT using the HCP-MMP1.0 parcellation of
      ~\cite{glasser2016multi}.}
      \label{fig:dice-thresh}
    \end{figure*}

>>>>

Further, from the thresholded maps, we determined regional instability 
between activation clusters in the 360 regions in the Human
Connectome Project Multi-Modal Parcellation atlas version 1.0
(HCP-MMP1.0)~\cite{glasser2016multi}. For BT, a region was unstable if it had different activation behavior between pair of tools.
For WT, we considered a region unstable if it had a blinking activation between Fuzzy samples of a given tool.

@@

We verified the correctness of our analyses by comparing our unperturbed
t-statistic group maps with the ones obtained
in~\cite{bowring2019exploring}. For FSL, we found
identical checksums. For SPM, the checksums were different but differences
were visually imperceptible. For AFNI, the activation maps were similar
overall, however, differences were more noticeable visually. 
Overall, our results correctly reproduced
the ones presented in~\cite{bowring2019exploring}. The observed
differences were small and might be due to the use of Octave vs MATLAB in
SPM or different hardware. We performed visual quality control of the AFNI and SPM results
for each individual subject.
\tristan{add a figure to show the differences for SPM (Octave) and AFNI}

@@

Summary statistics for the group-level unthresholded and thresholded
t-statistics are reported in Table~\ref{table:pipeline-stats}.
Overall, BT variability was larger than WT variability in both thresholded and unthresholded maps.
This was confirmed by computing the T-test and Wilcoxon signed-rank statistics between BT and WT as:

\begin{equation*}
  \left\{
    \begin{aligned}
      & BT(a, b), WT(a),\\
      & BT(a, b), WT(b)
    \end{aligned}  
    \quad  a,b \in [FSL, SPM, AFNI] \;
  \right\}
  \label{eq:t-tests}
\end{equation*}

We obtained statistically significant values between BT and WT
variability with t-value $> 70$ and p-value $< 0.05$.

%%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc|cc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Thresholded} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \cmidrule{5-6} \\
        {} & {} & Mean & Std. dev. & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  1.282       & 0.525      & 0.443     & 0.344  \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  1.548       & 0.616      & 0.547     & 0.441  \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  1.475       & 0.672      & 0.608     & 0.477  \\
        {Within Tool} & FSL                  &  0.354       & 0.491      & 0.082     & 0.065  \\
        {(WT)}   & SPM                       &  0.252       & 0.448      & 0.054     & 0.045  \\
        {}   & AFNI                          &  0.434       & 0.524      & 0.128     & 0.135  \\
        \bottomrule
    \end{tabular}
    \caption{Summary statistics of voxel-wise standard deviations
    in group-level t-statistics in BT and WT.}
    \label{table:pipeline-stats}
\end{table}

@@

  %%%%%%%%%% Summary of statstics %%%%%%%%
\setlength{\tabcolsep}{5pt}
\begin{table}[h]
    \centering
    \begin{tabular}{cccc}
        \toprule
        \multirow{2}{*}{}& {} & \multicolumn{2}{c}{Unthresholded} \\
        \cmidrule{3-4} \\
        {} & {} & Mean & Std. dev. \\
        \midrule
        \rowcolor{lightgray}
        {Between Tools} & FSL vs. SPM        &  0.366       & 0.293     \\
        \rowcolor{lightgray}
        {(BT)} & FSL vs. AFNI                &  0.439       & 0.352     \\
        \rowcolor{lightgray}
        {} & AFNI vs. SPM                    &  0.491       & 0.381     \\
        {Within Tool} & FSL                  &  0.077       & 0.054     \\
        {(WT)}   & SPM                       &  0.048       & 0.037     \\
        {}   & AFNI                          &  0.108       & 0.131     \\
        \bottomrule
    \end{tabular} 
    \caption{Summary statistics of voxel-wise standard deviations in subject-level t-statistics in BT and WT.
    The voxel-wise standard deviations were averaged across 16 subjects.}
    \label{table:unthresh-maps-subjects}
\end{table}

@@

  Similar conclusions are drawn from the unthresholded t-statistics maps
  (Figure~\ref{fig:thresh-maps}).
  Figure~\ref{fig:cm-thresh} compares instability of regional activations,
  showing that most of the regions have a similar activation pattern in both BT and WT, mostly are stable.
  However, some regions have a different activation behavior, mainly unstable in BT and stable in WT.
  % showing more severity of BT instability than WT.

  %%%%%%%%%% Var. of Thresh %%%%%%%%
  \begin{figure*}[ht]
      \fbox{\begin{minipage}{\dimexpr \textwidth-2\fboxsep-2\fboxrule}
        \centering
        \includegraphics[width=\textwidth]{figures/std/gl-thresh.png}
      \caption{Thresholded group t-statistics standard deviation maps
      computed across tools (\textbf{A}) and Fuzzy Libmath samples
      (\textbf{B}) as defined in Eq~\ref{eq:wt-pair}.}
      \label{fig:thresh-maps}
      \end{minipage}}
    \end{figure*}

    % %%%%%%%%%% Dice plot of thresholded tstats%%%%%%%%
    \begin{figure*}[ht]
      \centering
      \includegraphics[width=\textwidth]{figures/dice_analysis-plot.png}
      \caption{Heatmap of confusion matrices for instability of regional activations
      in BT and WT using the HCP-MMP1.0 parcellation of ~\cite{glasser2016multi}. 
      A region is unstable (=1) if it has different activation behavior in both tools
      for BT or different fuzzy samples in each tool for WT; otherwise, it is stable (=0).}
      \label{fig:cm-thresh}
    \end{figure*}
